Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 paper.tex
Adding new acknowledgments

JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, and NASA grant NNX17AG23G.  The freely available plotting library {\sc matplotlib} \citep{matplotlib} was used to construct numerous plots within this paper. Computations and analysis described in this work were performed using the publicly-available \enzo{} and \yt{} codes, which is the product of a collaborative effort of many independent scientists from numerous institutions around the world.

>>>>

JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, and NASA grant NNX17AG23G.  The simulation was performed on Blue
Waters operated by the National Center for Supercomputing Applications (NCSA) with PRAC allocation support by the NSF (awards ACI-1514580 and OAC-1810584). The subsequent analysis was performed with NSF's XSEDE allocation AST-120046 on the Comet resource and also on the Georgia Tech PACE compute system.  This research is part of the Blue Waters sustained-petascale computing project, which is supported by the NSF (awards OCI-0725070, ACI-1238993) and the state of Illinois. Blue Waters is a joint effort of the University of Illinois at Urbana-Champaign and its NCSA.  The freely available plotting library {\sc matplotlib} \citep{matplotlib} was used to construct numerous plots within this paper. Computations and analysis described in this work were performed using the publicly-available \enzo{} and \yt{} codes, which is the product of a collaborative effort of many independent scientists from numerous institutions around the world.
